On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-15 techreport.tex
This edit corresponds to the second item by Reviewer 1:
2) The model in this paper has some limitations. The authors did not =
consider some important issues in the platform, which are generally =
concerned in other papers, such as the number of tasks to be finished and =
the budget constraint of the platform to finish these tasks. When these =
issues are taken into consideration, the problem might become more =
difficult. Despite this, it is better to give an explanation or discussion =
on this, to make the proposed mechanism practical.

I have given some discussions on budget feasibility. Th

\section{Technical Preliminaries}
\label{sec:TP}
This section describes the technical preliminaries including the basics of crowdsensing game, the concept of equilibrium in game theory, and the idea of profit trading. We also give some useful local properties of bivariate functions in the appendix. Table \ref{tab:symbol_list} presents the frequently used symbols in this paper.\footnotetext[1]{Similarly, by removing subscripts, $t$ denotes the sensing time profile, $p$ denotes the payment profile, $u$ denotes the user utility profile, $n$ denotes the profile of number of tasks, etc.}
\begin{table}[!t]
\begin{tabular}{l l}
\toprule
Notation & Description\\
\hline
$U$ & the set of users\\
$n$ & the number of users: $|U|$ \\
%$R$ & the baseline gain of the platform\\
$s_i$ & the claimed cost unit (strategy) of user $i$\\
$s$ & the strategy profile of all users \footnotemark[1]\\
$s_{-i}$ & the strategy profile excluding user $i$'s strategy\\
$\kappa_i$ & the cost unit of user $i$\\
$p_i$ & the (promised) payment to user $i$\\
$t_i$ & the required sensing time of user $i$\\
$u_i$ & the utility function of user $i$\\
$u_p$ & the utility function of the platform\\
$n_i$ & number of the assigned tasks to user $i$\\
$m$	& number of partitions\\
$d$ & partition length\\
$f(x, y_0)$ & the slice function of $f(x,y)$ by fixing $y = y_0$\\
\bottomrule
\smallskip
\end{tabular}
\caption{Frequently used notations}
\label{tab:symbol_list}
\end{table}
\addtocounter{footnote}{1}

@@

We next analyze the platform utility. {Based on the ideas of \cite{yang2012crowdsourcing,luo2014profit,zhang2014free,liu2014social}}, the platform utility has a diminishing return on the contribution of each user. \cite{yan2015ifc} gives the idea to calculate the contributed gain from all the contributing users by summation over $U$. That is, we have its closed-form as following:
\begin{equation}
\label{eqn:plat_utility}
u_p=\sum_{i\in U}\lambda_i\log (1+t_i)-p_i.
\end{equation}
%Here $R$ is the baseline reward (i.e. the fixed reward as the crowdsensing finishes certain tasks).\footnote{In many existing models such as \cite{yang2012crowdsourcing}, there is no fixed baseline reward, and the gain primarily relies on the collected information. If so, $R=0$. If there are some external fundings provided by people who will use the collected information, then $R>0$.} {\color{black}As in Section \ref{sec:opu}, a positive baseline reward can well guarantee the participation of the platform, i.e. $R>0$.} $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing works, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working since it is making money.
Here $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing literatures, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working.
}

@@

\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1mm}
\begin{picture}(40,40)
\put (20,15){\circle{2}}
\put (16,12){\footnotesize$t_1=s_2\mathrm{e}^{-s_1}$}
\put (5,10){\circle{2}}
\put (0,7){\footnotesize$t_2=s_3\mathrm{e}^{-s_2}$}
\put (25,30){\circle{2}}
\put (27,30){\footnotesize$t_3=(s_1+s_4)\mathrm{e}^{-s_3}$}
\put (35,10){\circle{2}}
\put (30,7){\footnotesize$t_4=\mathrm{e}^{-s_4}$}
\put (5,35){\circle{2}}
\put (0,32){\footnotesize$t_5=\mathrm{e}^{-s_5}$}
\put (20,15){\vector(-3,-1){15}}
\put (5,10){\vector(1,1){20}}
\put (25,30){\vector(1,-2){10}}
\put (25,30){\vector(-1,-3){5}}
\end{picture}
\caption{\color{black}An example of parametric dependency graph. Here user 1 points to user 2, indicating user 1's utility $u_1$ is parametric dependent on user 2's strategy $s_2$, i.e. $u_1$ takes $s_2$ as input.}
\label{fig:pdg}
\end{figure}

@@

The platform assigns sensing tasks and computes the payment to each user based on the users' strategies. Each user will get the promised payment provided the assigned tasks are finished. Algorithm \ref{alg:np} gives the procedures for the platform to compute the number of assigned tasks and the promised payment for each user. 
{\color{black}We give our algorithm idea as follows:
\itemcount 1\relax
\bolditem Firstly we {\it partition} the cost unit interval $[0, +\infty)$. Our algorithm chooses the partition length $d$ as half of the minimum interval length of $[\underline{\kappa}_i, \overline{\kappa}_i]$, and chooses the number of partitions allowed by the maximum possible payment $P_m$. The platform will reduce the value of $d$ if $md$ is larger than the maximum possible cost unit. Then our algorithm divides $[0, +\infty)$ into $m+1$ partitions, with $m$ of them are of length $d$ and the rightmost one is $[md, +\infty)$. By doing this, none of the cost unit range intervals $K_i=[\underline{\kappa}_i, \overline{\kappa}_i]$ can completely reside within any partition here. Figure \ref{fig:d_idea} presents the resulted scenario by our choice of $d$. Small partition intervals may be beneficial to our truthful mechanism, as we will see later. 
\bolditem Then our algorithm computes $n_i$ and $p_i$ for each user $i$. The {\it higher} strategy $s_i$ the user claims, the {\it fewer} tasks will be assigned to the user. The payment is determined by which interval the strategy $s_i$ falls in. Figure \ref{fig:discrete_idea} gives the overview of our computation idea, i.e. the payment is the total area of the horizontal slices.
}

@@

Now we can show our main results, Theorem \ref{thm:discrete}.
\begin{theorem}
\label{thm:discrete}
For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given by Algorithm \ref{alg:np} can achieve group strategyproof and n-truthful equilibrium.
\end{theorem}
\begin{IEEEproof}
Clearly the utility of each user $i$ is not parametric dependent on any other user strategy. We may view $n_i$ as restricting the $t_i$ in (\ref{eqn:user_utility_2}) onto integers. %Then the statements in Theorem \ref{thm:main} and Theorem \ref{thm:pt} still hold for the case $u_i = p_i - \kappa_in_i$. 
Theorem \ref{thm:main} guarantees that to complete this proof, it suffices to show that the incentive mechanism given by Algorithm \ref{alg:np} can achieve strategyproof equilibrium. For any user $i$, to maximize its utility $u_i = p_i - \kappa_in_i$, $n_i$ must be $\max_{i\in U}\{m-\lfloor \kappa_i/d \rfloor, 0\}$ by Lemma \ref{lem:quadratic}. In other words, there will be no gain if user $i$ makes its strategy $s_i$ different from the true cost unit $\kappa_i$. This fact implies the strategyproof equilibrium.
\end{IEEEproof}
}
{\color{black}Note that there will be no gain or loss if user $i$ selects any other points within the ($m+1-n_i$)-th interval. Thus a small partition interval is beneficial to the truthful mechanism, since each user has less freedom to perturb the truthful strategy.}

>>>>

\section{Technical Preliminaries}
\label{sec:TP}
This section describes the technical preliminaries including the basics of crowdsensing game, the concept of equilibrium in game theory, and the idea of profit trading. We also give some useful local properties of bivariate functions in the appendix. Table \ref{tab:symbol_list} presents the frequently used symbols in this paper.\footnotetext[1]{Similarly, by removing subscripts, $t$ denotes the sensing time profile, $p$ denotes the payment profile, $u$ denotes the user utility profile, $n$ denotes the profile of number of tasks, etc.}
\begin{table}[!t]
\begin{tabular}{l l}
\toprule
Notation & Description\\
\hline
$U$ & the set of users\\
$n$ & the number of users: $|U|$ \\
%$R$ & the baseline gain of the platform\\
$s_i$ & the claimed cost unit (strategy) of user $i$\\
$s$ & the strategy profile of all users \footnotemark[1]\\
$s_{-i}$ & the strategy profile excluding user $i$'s strategy\\
$\kappa_i$ & the cost unit of user $i$\\
$p_i$ & the (promised) payment to user $i$\\
$t_i$ & the required sensing time of user $i$\\
$u_i$ & the utility function of user $i$\\
$u_p$ & the utility function of the platform\\
$n_i$ & number of the assigned tasks to user $i$\\
$m$	& number of partitions\\
$d$ & partition length\\
$f(x, y_0)$ & the slice function of $f(x,y)$ by fixing $y = y_0$\\
$B$ & budget, upper bound of the payment sum $\sum p_i$\\
\bottomrule
\smallskip
\end{tabular}
\caption{Frequently used notations}
\label{tab:symbol_list}
\end{table}
\addtocounter{footnote}{1}

@@

{\color{blue}
For the platform, we may consider the budget feasibility for many practical scenarios \cite{zhao2014crowdsource,singer2013pricing,singla2013truthful}. That is, the total sum of the payments $p_i$ must be no more than some budget $B$. In this paper, we will show that the payment sum of our proposed mechanisms can be upper bounded.
}
%We next analyze the platform utility. {Based on the ideas of \cite{yang2012crowdsourcing,luo2014profit,zhang2014free,liu2014social}}, the platform utility has a diminishing return on the contribution of each user. \cite{yan2015ifc} gives the idea to calculate the contributed gain from all the contributing users by summation over $U$. That is, we have its closed-form as following:
%\begin{equation}
%\label{eqn:plat_utility}
%u_p=\sum_{i\in U}\lambda_i\log (1+t_i)-p_i.
%\end{equation}
%%Here $R$ is the baseline reward (i.e. the fixed reward as the crowdsensing finishes certain tasks).\footnote{In many existing models such as \cite{yang2012crowdsourcing}, there is no fixed baseline reward, and the gain primarily relies on the collected information. If so, $R=0$. If there are some external fundings provided by people who will use the collected information, then $R>0$.} {\color{black}As in Section \ref{sec:opu}, a positive baseline reward can well guarantee the participation of the platform, i.e. $R>0$.} $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing works, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working since it is making money.
%Here $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing literatures, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working.
}

@@

\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1mm}
\begin{picture}(40,40)
\put (20,15){\color{black}\circle*{2.5}}
\put (16,12){\footnotesize$t_1=s_2\mathrm{e}^{-s_1}$}
\put (5,10){\circle*{2.5}}
\put (0,7){\footnotesize$t_2=s_3\mathrm{e}^{-s_2}$}
\put (25,30){\circle*{2.5}}
\put (27,30){\footnotesize$t_3=(s_1+s_4)\mathrm{e}^{-s_3}$}
\put (35,10){\circle*{2.5}}
\put (30,7){\footnotesize$t_4=\mathrm{e}^{-s_4}$}
\put (5,35){\circle*{2.5}}
\put (0,32){\footnotesize$t_5=\mathrm{e}^{-s_5}$}
\put (20,15){\large\vector(-3,-1){13.75}}
\put (5,10){\vector(1,1){18.75}}
\put (25,30){\vector(1,-2){9.25}}
\put (25,30){\vector(-1,-3){4.5}}
\end{picture}
\caption{\color{black}An example of parametric dependency graph. Here user 1 points to user 2, indicating user 1's utility $u_1$ is parametric dependent on user 2's strategy $s_2$, i.e. $u_1$ takes $s_2$ as input.}
\label{fig:pdg}
\end{figure}

@@

The platform assigns sensing tasks and computes the payment to each user based on the users' strategies. Each user will get the promised payment provided the assigned tasks are finished. Algorithm \ref{alg:np} gives the procedures for the platform to compute the number of assigned tasks and the promised payment for each user. 
{\color{black}We give our algorithm idea as follows:
\itemcount 1\relax
\bolditem Firstly we {\it partition} the cost unit interval $[0, +\infty)$. Our algorithm chooses the partition length $d$ as half of the minimum interval length of $[\underline{\kappa}_i, \overline{\kappa}_i]$, and chooses the number of partitions allowed by the maximum possible payment $P_m$, {\color{blue}which can be given by the budget $B$, i.e., $B\geq P_m\cdot n$}. The platform will reduce the value of $d$ if $md$ is larger than the maximum possible cost unit. Then our algorithm divides $[0, +\infty)$ into $m+1$ partitions, with $m$ of them are of length $d$ and the rightmost one is $[md, +\infty)$. By doing this, none of the cost unit range intervals $K_i=[\underline{\kappa}_i, \overline{\kappa}_i]$ can completely reside within any partition here. Figure \ref{fig:d_idea} presents the resulted scenario by our choice of $d$. Small partition intervals may be beneficial to our truthful mechanism, as we will see later. 
\bolditem Then our algorithm computes $n_i$ and $p_i$ for each user $i$. The {\it higher} strategy $s_i$ the user claims, the {\it fewer} tasks will be assigned to the user. The payment is determined by which interval the strategy $s_i$ falls in. Figure \ref{fig:discrete_idea} gives the overview of our computation idea, i.e. the payment is the total area of the horizontal slices.
}

@@

Now we can show our main results, Theorem \ref{thm:discrete}.
\begin{theorem}
\label{thm:discrete}
For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given by Algorithm \ref{alg:np} can achieve group strategyproof and n-truthful equilibrium.
\end{theorem}
\begin{IEEEproof}
Clearly the utility of each user $i$ is not parametric dependent on any other user strategy. We may view $n_i$ as restricting the $t_i$ in (\ref{eqn:user_utility_2}) onto integers. %Then the statements in Theorem \ref{thm:main} and Theorem \ref{thm:pt} still hold for the case $u_i = p_i - \kappa_in_i$. 
Theorem \ref{thm:main} guarantees that to complete this proof, it suffices to show that the incentive mechanism given by Algorithm \ref{alg:np} can achieve strategyproof equilibrium. For any user $i$, to maximize its utility $u_i = p_i - \kappa_in_i$, $n_i$ must be $\max_{i\in U}\{m-\lfloor \kappa_i/d \rfloor, 0\}$ by Lemma \ref{lem:quadratic}. In other words, there will be no gain if user $i$ makes its strategy $s_i$ different from the true cost unit $\kappa_i$. This fact implies the strategyproof equilibrium.
\end{IEEEproof}
}
{\color{black}Note that there will be no gain or loss if user $i$ selects any other points within the ($m+1-n_i$)-th interval. Thus a small partition interval is beneficial to the truthful mechanism, since each user has less freedom to perturb the truthful strategy. }
{\color{blue}Also our mechanism is budget feasible, since the payment sum is upper bounded by the budget B, i.e., $\sum_{p_i} < P_m\cdot n \leq B$.}
